### 2019-04-29 papers/haskell19/6-casestudies.tex
Added case studies

>>>>

\begin{tikzpicture}
  \begin{axis}
    [ ybar
    , enlargelimits=0.15
    , enlarge x limits=0.3
    , /pgf/bar width=15pt
    , legend style={
        at={(0.5,-0.15)},
        anchor=north,legend columns=3}
    , ylabel={Relative Generation Time}
    , symbolic x coords={SExp, RBT, Html}
    , xtick=data
    % , nodes near coords
    , nodes near coords align={vertical}
    ]
    \addplot[fill, red!30]   coordinates {(SExp,1)    (RBT,1)    (Html,1)};
    \addplot[fill, green!30] coordinates {(SExp,2.31) (RBT,3)    (Html,4.88)};
    \addplot[fill, blue!30]  coordinates {(SExp,1.62) (RBT,2.28) (Html,1.70)};
    \legend{Manual, Modular/Linear, Modular/Balanced}
\end{axis}
\end{tikzpicture}
